Leveraging Diversity to Find Bugs\\ in JavaScript Engines

### 2018-08-25 paper/paper.tex
pass on conclusion

\subsection{Lessons Learned}

@@

@@

\Mar{----------------------------- estou aqui $\rightarrow$}

%\section*{Acknowledgment}

%\bibliographystyle{IEEEtran}
\balance
\bibliographystyle{plain}
\bibliography{references,../docs/google-research-awards-latam/tmp}

>>>>

\subsection{Lessons Learned}
\label{sec:lessons}

@@

%%%%%%%%%%%%%%%%%%%%%%%
%%% comentario de igor
%%%%%%%%%%%%%%%%%%%%%%%
%% sim, me refiro a testes que possuem algum comentário do que se trata aquele teste. Por exemplo os testes262, possuem comentários descrevendo o que o teste tem que fazer
%% os testes da suite do mozilla são mais dificeis de debuggar... não dificeis de grosso modo, mas custava um pouco para identificar o real problema

@@

JavaScript is a very popular language. For that reason, bugs in engine
implementations often affect lots of people and organizations.
Implementing correct engines is challenging because the specification
is intentionally incomplete and evolves frequently. Finding bugs is
challenging for similar reasons. We conducted a study to evaluate two
simple diversity-aware techniques--test transplantation and
cross-engine differential testing. The first technique runs test
suites of a given engine in another engine. The second technique
fuzzes existing inputs and then compares the output produced by
different engines with a differential oracle.

Overall, we reported \Fix{XX} bugs in this study. Of which, \Fix{YY}
were confirmed and \Fix{ZZ} were fixed by developers. Although more
work is necessary to reduce cost of manual analysis, we found that
both techniques we used are effective at finding bugs in the engines
used in the most popular we browsers used
today. Section~\ref{sec:lessons} elaborates on the lessons we learned
in this study. The result data, the infrastructure, and experimental
scripts we prepared to run this study are available upon request.

\balance
\bibliographystyle{plain}
\bibliography{references,../docs/google-research-awards-latam/tmp}
